\bf Manifold Clustering in the Generalized Random Dot Product Graph

### 2022-05-04 draft/draft.Rmd
still working on it

```{r example1, fig.cap = 'Manifold block model described in Example 1. The latent configuration is on the left, and a random dot product graph drawn from the latent configuration is on the middle, and the ASE is on the right.', fig.height = 2.5, fig.width = 7}
set.seed(123456)
n1 <- 2 ** 5
n2 <- 2 ** 5
n <- n1 + n2
z <- c(rep(1, n1), rep(2, n2))
u1 <- runif(n1)
u2 <- runif(n2)
x1 <- cos(pi / 3 * u1)
y1 <- sin(pi / 3 * u1)
x2 <- 1 + cos(pi / 3 * u2 + pi)
y2 <- 1 + sin(pi / 3 * u2 + pi)
data.matrix <- cbind(c(x1, x2), c(y1, y2))
A <- draw.graph(data.matrix %*% t(data.matrix))
Xhat <- embedding(A, 2, 0)

@@

\begin{lemma}
\label{lem:one-hypercube}
Let $x_1, ..., x_n \iid F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $H_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected for any $\eta > 0$. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon + r \log \eta - \frac{r}{2} \log r}{\log (1 - a \eta^r r^{-r / 2})} \bigg)$ such that $P(E_n) > 1 - \epsilon$ when $n \geq N$.
\end{lemma}

@@

@@

>>>>

```{r example1, fig.cap = 'Manifold block model described in Example 1. The latent configuration is on the left, a random dot product graph drawn from the latent configuration is on the middle, and the ASE is on the right.', fig.height = 2.5, fig.width = 7}
set.seed(123456)
n1 <- 2 ** 5
n2 <- 2 ** 5
n <- n1 + n2
z <- c(rep(1, n1), rep(2, n2))
u1 <- runif(n1)
u2 <- runif(n2)
x1 <- cos(pi / 3 * u1)
y1 <- sin(pi / 3 * u1)
x2 <- 1 + cos(pi / 3 * u2 + pi)
y2 <- 1 + sin(pi / 3 * u2 + pi)
data.matrix <- cbind(c(x1, x2), c(y1, y2))
A <- draw.graph(data.matrix %*% t(data.matrix))
Xhat <- embedding(A, 2, 0)

@@

\begin{lemma}
\label{lem:one-hypercube}
Let $x_1, ..., x_n \iid F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $H_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected for any $\eta > 0$. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon + r \log \eta - \frac{r}{2} \log r}{\log (1 - a \eta^r r^{-r / 2})} \bigg)$ such that $P(H_n) > 1 - \epsilon$ when $n \geq N$.
\end{lemma}

@@

Lemma \ref{lem:one-hypercube} extends to the case in which vectors are drawn from hypercubes with noise, given that the noise is bounded.

\begin{lemma}
\label{lem:one-hypercube-noise}
Suppose the setup from lemma \ref{lem:one-hypercube}, but instead of observing each $x_i$, we observe each $y_i = x_i + e_i$ for some $e_1, ..., e_n \in \mathbb{R}^d$. 
Let $\nu = \max_i \|e_i\| < \infty$ be bounded. 
Define $\tilde{H}_n$ as the event in which an $(\eta + 2 \nu)$-neighborhood graph constructed from sample $y_1, ..., y_n$ is connected. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon + r \log \eta - \frac{r}{2} \log r}{\log (1 - a \eta^r r^{-r / 2})} \bigg)$ such that $P(\tilde{H}_n) > 1 - \epsilon$ when $n \geq N$.
\end{lemma}

\begin{proof}
\end{proof}

@@

It can similarly be shown that the scenario in lemma \ref{lem:K-hypercubes} with bounded noise can be achieved by replacing the $\eta$-neighborhood graph with an $(\eta + 2 \nu)$-neighborhood graph, where $\nu = \max_i \|e_i\|$. 
This time, it is necessary to bound the noise as $\nu < \delta / 3$ to maintain separation between the hypercubes.

### 2022-05-04 draft/draft.tex
still working on it

\caption{Manifold block model described in Example 1. The latent configuration is on the left, and a random dot product graph drawn from the latent configuration is on the middle, and the ASE is on the right.}\label{fig:example1}
\end{figure}
\end{example}

@@

\begin{lemma}
\label{lem:one-hypercube}
Let $x_1, ..., x_n \stackrel{\mathrm{iid}}{\sim}F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $H_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected for any $\eta > 0$. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon + r \log \eta - \frac{r}{2} \log r}{\log (1 - a \eta^r r^{-r / 2})} \bigg)$ such that $P(E_n) > 1 - \epsilon$ when $n \geq N$.
\end{lemma}

@@

>>>>

\caption{Manifold block model described in Example 1. The latent configuration is on the left, a random dot product graph drawn from the latent configuration is on the middle, and the ASE is on the right.}\label{fig:example1}
\end{figure}
\end{example}

@@

\begin{lemma}
\label{lem:one-hypercube}
Let $x_1, ..., x_n \stackrel{\mathrm{iid}}{\sim}F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $H_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected for any $\eta > 0$. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon + r \log \eta - \frac{r}{2} \log r}{\log (1 - a \eta^r r^{-r / 2})} \bigg)$ such that $P(H_n) > 1 - \epsilon$ when $n \geq N$.
\end{lemma}

@@

It can similarly be shown that the scenario in lemma
\ref{lem:K-hypercubes} with bounded noise can be achieved by replacing
the \(\eta\)-neighborhood graph with an \((\eta + 2 \nu)\)-neighborhood
graph, where \(\nu = \max_i \|e_i\|\). This time, it is necessary to
bound the noise as \(\nu < \delta / 3\) to maintain separation between
the hypercubes.
